Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2021-09-30 mice_synthesizing/paper.Rmd
Restructure pooling rules section.

@@

To assess the performance of `mice` for synthesizing data, we compare the bootstrapped samples with the synthetic versions of these bootstrapped samples. Specifically, univariate descriptive statistics, the correlation matrix, and two linear regression models as well as one ordered logistic regression model will be considered. Subsequently, the bias in the parameters and the $95\%$ confidence interval coverage of the synthetic data will be examined. Similarly to multiple imputation of missing data, $95\%$ confidence intervals must be calculated using an adjusted variance estimator that accounts for the increase in variance due to imputation [@reiter_partially_inference_2003; @drechsler_synthetic_2011]. However, these variance estimators are not the same. Whereas the variance estimate after imputation of missing data needs to account for the fact that a certain amount of information in the data is missing, variance estimation from synthetic data does not suffer from this issue. The adjusted variance estimate that follows from using multiple synthetic datasets only suffers from the fact that a finite number of $m$ synthetic datasets are used to resemble the observed data. Hence, the according pooling rules for synthetic data as developed by @reiter_partially_inference_2003 are

\begin{aligned}

\bar{q}_m &= \sum_{l = 1}^m \frac{q^{(l)}}{m}, \\

b_m       &= \sum_{l = 1}^m \frac{(q^{(l)} - \bar{q}_m)^2}{(m - 1)}, \\

\bar{u}_m &= \sum_{l = 1} \frac{u^{(l)}}{m}.

\end{aligned}

>>>>

## Simulation methods

@@

To assess the performance of `mice` for synthesizing data, we compare the bootstrapped samples with the synthetic versions of these bootstrapped samples. Specifically, univariate descriptive statistics, the correlation matrix, and two linear regression models as well as one ordered logistic regression model will be considered. Subsequently, the bias in the parameters and the $95\%$ confidence interval coverage of the synthetic data will be examined. Similarly to multiple imputation of missing data, correct inferences from synthetic data requires correct pooling over the multiply imputed datasets.

Obtaining a final point estimate of the parameter of interest $Q$ after imputation is fairly easy and no different from pooling in the case of missing data [@rubin_multiple_1987]. One can calculate the average of the $m$ point estimates $q^{(l)}$
$$
\bar{q}_m = \sum_{l = 1}^m \frac{q^{(l)}}{m}.
$$
Also similarly to the missing data case, variances, and subsequently confidence intervals, should incorporate the increase in variance that is due to imputation [@reiter_partially_inference_2003; @drechsler_synthetic_2011]. Yet, the increase in variance due to imputation differs according to whether missing values are imputed or observed data is overimputed with missing values. Whereas the variance estimate after imputation of missing data needs to account for the fact that a certain amount of information in the data is missing, variance estimation from synthetic data does not suffer from this issue. The adjusted variance estimate that follows from using multiple synthetic datasets only suffers from the fact that a finite number of $m$ synthetic datasets are used to resemble the observed data. Hence, the according variance estimate for synthetic data as developed by @reiter_partially_inference_2003 yields
$$
T = \bar{u}_m + \frac{b_m}{m},
$$
with "between-imputation" variance

$$
b_m = \sum_{l = 1}^m \frac{(q^{(l)} - \bar{q}_m)^2}{(m - 1)}, \\
$$
and "within-imputation" variance
$$
\bar{u}_m = \sum_{l = 1} \frac{u^{(l)}}{m},
$$
with $u^{(l)}$ reflecting the variance estimate in every imputed dataset.

## Simulation results
